---
title: "Bootstrap Resample Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bootstrap-vingette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
nocite: "@*"
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = FALSE, message = FALSE}
if (!require("BootstrapResample")) remotes::install_github("j-gdb/sta380-Project")
```

```{r setup}
library(BootstrapResample)
```

# Introduction
This package provides a simple way to compute the mean and IQR of univariate data. It comes with some helper functions to get this done. This vignette serves as an example of how to use the libraries.

Bootstrap resampling works by taking the original dataset with length $n$, and randomly sampling $n$ observations from that dataset with replacement, computing a desired statistic. This is done many times, producing a distribution for the statistic we are trying to estimate.

# Bootstrap Resampling for Mean and IQR.

## Loading Sample Data
We can use a sample dataset, such as the `mtcars` dataset. We will be using the miles per gallon column for this example.
```{r}
data("mtcars")
x = mtcars$mpg
```

## Bootstrap Resampling for the Mean
For this example, we will resample from the dataset 1000 times. By default, this package will resample 5000 times. The functions also allow for you to pass in a random seed. Otherwise, it will be fixed to the seed `1`. For this example, we will use the seed `42`.
```{r}
true_mean = mean(x)
boot_means = bootstrap_means(x, num_samples = 1000, seed = 42)
```

We can plot the distribution in a histogram, and compare it to the true mean, denoted by the red line.
```{r, fig.width=7, fig.height=5}
hist(boot_means,
     main = "Bootstrap Distribution of Means for Miles Per Gallon",
     xlab = "Bootstrap Means",
     col = "skyblue",
     prob = TRUE)
abline(v = true_mean, col = "red", lwd = 2)
```

## Bootstrap Resampling for IQR
Again, for this example, we will resample from the dataset 1000 times, and use the random seed `42`.
```{r}
true_IQR = IQR(x)
boot_IQR = bootstrap_IQR(x, num_samples = 1000, seed = 42)
```

We can plot the distribution in a histogram, and compare it to the true IQR, denoted by the red line.
```{r, fig.width=7, fig.height=5}
hist(boot_IQR,
     main = "Bootstrap Distribution of IQR for Miles Per Gallon",
     xlab = "Bootstrap IQR",
     col = "green",
     prob = TRUE)
abline(v = true_IQR, col = "red", lwd = 2)
```

# Generative AI Statement
We have used generative AI to help us set up the development environment, such as creating it as an R project and debugging errors when trying to generate the roxygen comments. We also used generative AI to help fix warnings, such as adding imports and editing the DESCRIPTION file, and adding the license.

# References
